Monte Carlo calculation to characterize neutron and gamma fields for ANITA neutron facility at TSL

### 2015-04-17 Paper2015.tex
Introduced a combined figure for CUP and SUP spectra, and removed separate figures.

@@

\begin{figure}[t]
    \begin{minipage}{\columnwidth}
        \centering
        \includegraphics[width=0.9\columnwidth]{SUPComparedIFluxRADECS.eps}
        \subcaption{Integral fluence rate}
    \end{minipage}
    \begin{minipage}{\columnwidth}
        \centering
        \includegraphics[width=0.9\columnwidth]{SUPNormalisedRADECS.eps}
        \subcaption{Equilethargic spectrum, normalised to fluence above \SI{10}{\MeV}}
    \end{minipage}
	\caption{
        Neutron spectrum at the SUP, showing comparison between the standard facility parameterisation~\cite{Prokofiev2009} and results from a naked Geant4 model~\cite{Platt13} and this work.
    }
	\label{fig:SUPSpectraComparison}
\end{figure}

@@

\begin{figure}[t]
    \begin{minipage}{\columnwidth}
        \centering
        \includegraphics[width=0.9\columnwidth]{ANITAIntYieldRADECS.eps}
        \subcaption{Integral fluence rate}
    \end{minipage}
    \begin{minipage}{\columnwidth}
        \centering
        \includegraphics[width=0.9\columnwidth]{ANITALetYieldnormalisedRADECS.eps}
    	\subcaption{Equilethargic spectrum, normalised to fluence above \SI{10}{\MeV}}
    \end{minipage}
	\caption{
        Neutron spectrum at the Close User Position, showing comparison between the standard facility parameterisation~\cite{Prokofiev2009} and results from this work.
    }
	\label{fig:CUPSpectraComparison}
\end{figure}

>>>>

Fig.~\ref{fig:Lethargyplots}

\begin{figure}[t]
    \begin{minipage}{\columnwidth}
        \centering
        \includegraphics[width=0.9\columnwidth]{SUPNormalisedRADECS.eps}
        \subcaption{
            SUP.
            The comparison is against preliminary Geant4 modelling with a naked target model~\cite{Platt13} and against the standard facility parameterisation~\cite{Prokofiev2009}
        }
    \end{minipage}
    \begin{minipage}{\columnwidth}
        \centering
        \includegraphics[width=0.9\columnwidth]{ANITALetYieldnormalisedRADECS.eps}
        \subcaption{
            CUP. 
            The comparison is against the standard facility parameterisation~\cite{Prokofiev2009}
        }
    \end{minipage}
	\caption{
        Calculated neutron spectra, normalised to fluence above \SI{10}{\MeV}
    }
	\label{fig:Lethargyplots}
\end{figure}

@@

@@
